Measurement and Probability in Fuzzy Quantum Theories

### 2017-01-30 prop.tex
prop.tex \section{Quantum Interval-valued Probability Measures} Fix typos...
prop.tex \section{Increasing the Measurement Resource} Fix typos...

\begin{definition}
  Given a quantum interval-valued probability
  measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core} of $\bar{\mu}$ is the set
  $\mathrm{core}\left(\bar{\mu}\right)=\left\{
    \pmeas:\events\rightarrow[0,1] ~\middle|~ \forall
    E\in\events.~\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\}$.
\item $\bar{\mu}$ is called convex if
  $\bar{\mu}\left(P_{0}\vee
    P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
  for all commuting $P_{0},P_{1}\in\events$.
\end{itemize}
\end{definition}

@@

\begin{example}[Three-dimensional quantum three-interval-valued 
  probability measure]\label{ex:three-dimensional-three-value} Given
  a three dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
    $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $},
  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
  $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$, and
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})
  &=& \imposs\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})
  &=& \necess \\
\bar{\mu}(P) 
  &=& \unknown\quad\textrm{otherwise}
\end{eqnarray*}
It is straightforward to verify that $\bar{\mu}$ is a convex quantum
interval-valued probability measure. Now assume there exists a
real-valued quantum probability measure $\mu$ such that
$\mu(P)\in\bar{\mu}(P)$ for every event (projection)~$P$. We derive a
contradiction as follows. Suppose $\mu(P)\in\bar{\mu}(P)$ then we must
have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$. By Gleason's
theorem, there is a mixed
state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$ such that
$\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$, where
$\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$.  However, no pure
state~$\ket{\phi}$ can satisfy
$\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
\end{example}

@@

\begin{lemma}A interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the following properties:
\begin{itemize}
\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
we have $1\in\sum_{i=0}^{2}\bar{f}\left(\ket{\psi_{i}}\right)$ and
$\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
where $i$, $j$, and $k$ are any permutations among $0$, $1$,
and $2$.
\end{itemize}
Conversely, if a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties, $\bar{f}$ must be an interval-valued
frame function.\end{lemma}
\begin{proof}
Given a quantum IVPM~$\bar{\mu}$, it is straightforward to verify
that its interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties.

>>>>

\begin{definition}
  Given a quantum interval-valued probability
  measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$. 
\item $\bar{\mu}$ is called convex if
  $\bar{\mu}\left(P_{0}\vee
    P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
  for all commuting $P_{0},P_{1}\in\events$.
\end{itemize}
\end{definition}

@@

\begin{example}[Three-dimensional quantum three-interval-valued
probability measure]\label{ex:three-dimensional-three-value} Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
$\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$, and 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\\
\bar{\mu}(P) & = & \unknown\quad\textrm{otherwise}
\end{eqnarray*}
It is straightforward to verify that $\bar{\mu}$ is a convex quantum
interval-valued probability measure. Now assume there exists a real-valued
quantum probability measure $\mu$ such that $\mu(P)\in\bar{\mu}(P)$
for every event (projection)~$P$. We derive a contradiction as follows.
Suppose $\mu(P)\in\bar{\mu}(P)$ then we must have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$.
By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
can satisfy $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
\end{example}

@@

\begin{lemma}An interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the following properties:
\begin{itemize}
\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
we have $1\in\sum_{i=0}^{2}\bar{f}\left(\ket{\psi_{i}}\right)$ and
$\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
where $i$, $j$, and $k$ are any permutations among $0$, $1$,
and $2$.
\end{itemize}
Conversely, if a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties, $\bar{f}$ must be an interval-valued
frame function.\end{lemma}
\begin{proof}
Given a quantum IVPM~$\bar{\mu}$, it is straightforward to verify
that its interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties.
